{{< var titll >}}

### 2024-07-20 addendum/Addendum_ne.qmd
nevada

---
title: "{{< var addas >}}"
subtitle: "{{< var addal >}}"
format:
  revealjs: 
    smaller: true
    toc-depth: 1
    toc: true 
execute: 
  cache: false
footer: <https://lotariohw26.github.io/ManifoldDestiny/>
output: 
  html_document:
    mathjax: "https://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML"
nocite: |
  @*
---

```{r}
knitr::knit_exit()
```

```{r, echo=F, warning=F, message=F}
library(ManifoldDestiny)
library(RefManageR)
library(huxtable)
library(plotly)
xaringanExtra::use_editable(expires = 1)
xaringanExtra::use_tile_view()
xaringanExtra::use_share_again()
xaringanExtra::use_scribble()
xaringanExtra::use_webcam()
xaringanExtra::use_panelset()
modlat <- eqpar$meql
labs <- stickers[['parameters']]
abs_p <- rprojroot::find_rstudio_root_file()
#source(paste0(rprojroot::find_rstudio_root_file(),'/inst/script/addendum_az.R'))
```

```{r, eval=F, echo=F, message=F, warning=F}
pre_fil <- paste0(rprojroot::find_rstudio_root_file(),'/inst/www/addendum/Addendum_ne.Rmd')
xaringan::inf_mr(pre_fil)
#rmarkdown::render(pre_fil) 
```

```{r}
knitr::knit_exit()
```

---
title: "Nevada"
output:
  bookdown::html_document2: default
# https://docs.google.com/document/d/13u3lL_emHyLpog-rFrm7-zk7lKM_AmQd28CJlJ5odFE/edit#
---

```{r}
source(paste0(rprojroot::find_rstudio_root_file(),'/inst/script/addendum_ne.R'))
```

# Introduction

![](pngs/necawa.png)

[$50,000 Reward!](https://operationsunlight.com/2022/11/26/50000-reward/)

```{r}
plotly::plot_ly(bindf, x = ~g, y = ~h, z = ~alpha, color = ~tpg,
        type = "scatter3d", mode = "markers")
```

# Main results

# Sideeffects

## Sideeffect #1

```{r}
abc <- allreport(fir$sdfc)
abc[[1]][[2]][[4]]
```

```{r}
abc <- allreport(sec$sdfc)
abc[[1]][[2]][[4]]
```
## Sideeffect #2
## Sideeffect #3
## Sideeffect #4

>>>>

---
title: "{{< var addnl >}}"
format: 
  html:
    toc: true
    toc-depth: 3
    number-sections: false
---

```{r}
#| echo: false
#| output: false
#| message: false
#| warning: false
options(digits=2)
ManifoldDestiny::wasmconload()
apps <- appn1
adat <- apps[[1]]
amet <- apps[[2]]
cogr <- Countinggraphs(apps[[1]])
selo <- seloutput(selreport(apps))
copl <- cogr$polyc[[1]][[1]]
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
```

### Without purge

::: {.panel-tabset}

### {{< var tabs.h1 >}}

```{r, echo=F}
kableExtra::kbl(selo[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```
### {{< var tabs.h2 >}}
```{r, echo=F, out.width="60%"}
selo[['corxy']]
```
### {{< var tabs.h3 >}}
```{r, echo=F, out.width="60%"}
selo[['qunt']]
```
### {{< var tabs.h4 >}}
```{r, echo=F}
selo[['ro3d']]
```
### {{< var tabs.h5 >}}
```{r, echo=F, out.width="60%"}
selo[['regr']]
```
### {{< var tabs.h6 >}}
```{r, echo=F, out.width="60%"}
selo[['cmp']]
```
### {{< var tabs.h7 >}}
```{r, echo=F, out.width="60%"}
selo[['resp']]
```
:::

### With purge

```{r}
#| echo: false
#| output: false
#| message: false
#| warning: false
options(digits=2)
ManifoldDestiny::wasmconload()
apps <- appn1
adat <- apps[[1]]
amet <- apps[[2]]
amet$prg$z <- 0
cogr <- Countinggraphs(apps[[1]])
selo <- seloutput(selreport(apps))
copl <- cogr$polyc[[1]][[1]]
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmconverting.R"))
source(paste0(rprojroot::find_rstudio_root_file(),"/R/wasmnonverting.R"))
```

::: {.panel-tabset}

### {{< var tabs.h1 >}}

```{r, echo=F}
kableExtra::kbl(selo[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```
### {{< var tabs.h2 >}}
```{r, echo=F, out.width="60%"}
selo[['corxy']]
```
### {{< var tabs.h3 >}}
```{r, echo=F, out.width="60%"}
selo[['qunt']]
```
### {{< var tabs.h4 >}}
```{r, echo=F}
selo[['ro3d']]
```
### {{< var tabs.h5 >}}
```{r, echo=F, out.width="60%"}
selo[['regr']]
```
### {{< var tabs.h6 >}}
```{r, echo=F, out.width="60%"}
selo[['cmp']]
```
### {{< var tabs.h7 >}}
```{r, echo=F, out.width="60%"}
selo[['resp']]
```
:::

[Spreadsheet calculation (Solomon)](https://docs.google.com/spreadsheets/d/1gkf41sJRAQ6bwKmlAAcb7hAQ6v4zIXG2wDYl67LrJ4k/edit?gid=59123130#gid=59123130)

```{r, echo=F}
knitr::knit_exit()
```

### 2024-07-20 paper.qmd
nevada

```{r}
ManifoldDestiny::wasmconload()
library(ManifoldDestiny)
library(huxtable)
library(kableExtra)
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
```

@@

## {{< var sec3.un1 >}}
```{r}
#| echo: false
#| output: false
apps <- basc
```
{{< include tabpar.qmd >}}

## {{< var sec3.un2 >}}
### Normal form
```{r}
#| echo: false
#| output: false
apps <- rigv[[1]]
```
{{< include tab.qmd >}}

@@

### Opposition
```{r}
#| echo: false
#| output: false
apps <- rigv[[3]]
```

>>>>

```{r, echo=F}
ManifoldDestiny::wasmconload()
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
```

```{r}
#| echo: false
#| output: false
apps <- appn1
```
{{< include tabpar.qmd >}}

```{r}
knitr::knit_exit()
```

@@

## {{< var sec3.un1 >}}
```{r}
#| echo: false
#| output: false
apps <- appsn
```
{{< include tabpar.qmd >}}

```{r}
knitr::knit_exit()
```

## {{< var sec3.un2 >}}
### Normal form
```{r}
#| echo: false
#| output: false
apps <- apprn
```
{{< include tab.qmd >}}

@@

### Opposition
```{r}
#| echo: false
#| output: false
apps <- appro
```

### 2024-07-20 tab.qmd
nevada

```{r, echo=F}
kableExtra::kbl(selo[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```
### {{< var tabs.h2 >}}
```{r, echo=F, out.width="60%"}
selo[['corxy']]
```
### {{< var tabs.h3 >}}
```{r, echo=F, out.width="60%"}
selo[['qunt']]
```
### {{< var tabs.h4 >}}
```{r, echo=F}
selo[['ro3d']]
```
### {{< var tabs.h5 >}}
```{r, echo=F, out.width="60%"}
selo[['regr']]
```
### {{< var tabs.h6 >}}
```{r, echo=F, out.width="60%"}
selo[['resp']]
```
:::

>>>>

```{r, echo=F}
kableExtra::kbl(selo[['decs']]) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::kable_styling(font_size=8)
```
### {{< var tabs.h2 >}}
```{r, echo=F, out.width="60%"}
selo[['corxy']]
```
### {{< var tabs.h3 >}}
```{r, echo=F, out.width="60%"}
selo[['qunt']]
```
### {{< var tabs.h4 >}}
```{r, echo=F}
selo[['ro3d']]
```
### {{< var tabs.h5 >}}
```{r, echo=F, out.width="60%"}
selo[['regr']]
```
### {{< var tabs.h6 >}}
```{r, echo=F, out.width="60%"}
selo[['cmp']]
```
### {{< var tabs.h7 >}}
```{r, echo=F, out.width="60%"}
selo[['resp']]
```
:::
